MSGenova (Clean version) Rmakrdown Report

### 2022-09-14 script/ms_report.Rmd
update report and add extract_flagstat rule

```{r setup, include=FALSE}
workspace<-"/home/gabriele.adam/Documents/Msgenova/sorties_report/results"
knitr::opts_chunk$set(root.dir=workspace, echo = FALSE , warning=FALSE, error=FALSE, message=FALSE)
```

>>>>

```{r setup, include=FALSE}
workspace<-params$result_dir
knitr::opts_chunk$set(root.dir=workspace, echo = FALSE , warning=FALSE, error=FALSE, message=FALSE)
```
